---
title: "Bike Sharing Demand"
author: "Akshay Terode"
date: "15 November 2018"
output: html_document
---
### Data Fields : 
* **datetime -** hourly date + timestamp  
* **season -**  1 = spring, 2 = summer, 3 = fall, 4 = winter 
* **holiday -** whether the day is considered a holiday
* **workingday -** whether the day is neither a weekend nor holiday
* **weather -** 
  * *1:* Clear, Few clouds, Partly cloudy, Partly cloudy 
  * *2:* Mist + Cloudy, Mist + Broken clouds, Mist + Few clouds, Mist 
  * *3:* Light Snow, Light Rain + Thunderstorm + Scattered clouds, Light Rain + Scattered clouds 
  * *4:* Heavy Rain + Ice Pallets + Thunderstorm + Mist, Snow + Fog 
* **temp -** temperature in Celsius
* **atemp -** "feels like" temperature in Celsius
* **humidity -** relative humidity
* **windspeed -** wind speed
* **casual -** number of non-registered user rentals initiated
* **registered -** number of registered user rentals initiated
* **count -** number of total rentals
```{r}
bikeshare <- read.csv ("/home/student/RCodes/Stats With R/Datasets/all/train.csv")
head(bikeshare)
```
#### Checking wheter data frame has any missing value
```{r}

```

```{r}
bike <- bikeshare[,-c(1,10,11)]
bike$season <- factor(bike$season,levels = c(1,2,3,4),labels = c("spring","summer","fall","winter"))
bike$weather <- factor(bike$weather)
```
```{r}
fit.lm <- lm(count ~. ,data = bike)
summary(fit.lm)
```
### For test dataset
```{r}
bikesharetest <- read.csv ("/home/student/RCodes/Stats With R/Datasets/all/test.csv")
head(bikesharetest)
biketest <- bikesharetest[,-1]
biketest$season <- factor(biketest$season,levels = c(1,2,3,4),labels = c("spring","summer","fall","winter"))
biketest$weather <- factor(biketest$weather)
pred_lm <- predict(fit.lm,newdata = biketest)
pred_lm
```

